### 2019-07-26 manuscript_clean.Rmd
redid VCV comparisons without transforming NA->zero and contrasting each regime against its preceding one, not the whole tree matrix

*Evolution of nematocyst shape* – Haploneme nematocyst evolution has been mainly driven by a single large shift towards elongation in Tendiculophora, which contains the majority of described siphonophore species. There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it doesn't reach the sphericity present in Cystonectae or Pyrostephidae (Fig. \@ref(figure10)). Heteroneme evolution presents a less radical evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal. In this group, the evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape, which has remained fairly constant (elongation between 1.5 and 2.5).

>>>>

*Evolution of nematocyst shape* – Haploneme nematocyst evolution has been mainly driven by a single large shift towards elongation in Tendiculophora, which contains the majority of described siphonophore species. There is one secondary return to more oval, less elongated haplonemes in *Erenna*, but it does not reach the sphericity present in Cystonectae or Pyrostephidae (Fig. \@ref(figure10)). Heteroneme evolution presents a less radical evolutionary history, where Tendiculophora evolved more elongate heteronemes, but the difference between theirs and other siphonophores is much smaller than the variation in shape within Tendiculophora, bearing no phylogenetic signal. In this group, the evolution of heteroneme shape has diverged in both directions, and there is no correlation with haploneme shape, which has remained fairly constant (elongation between 1.5 and 2.5).
